\textbf{SPECFEM3D Cartesian}\\ \textbf{User Manual}

### 2013-07-08 doc/USER_MANUAL/manual_SPECFEM3D_Cartesian.tex
two more logos (again)
added one more logo
better copyright information

\author{$\copyright$ Princeton University (USA),\\
CNRS and University of Marseille (France),\\
and ETH Z\"urich (Switzerland)\\
Version 2.1}

@@

\noindent \begin{centering}
\includegraphics[width=0.15\textwidth]{figures/logo_NVIDIA}\vspace*{2truemm}
\includegraphics[width=0.125\textwidth]{figures/logo_IUF}\vspace*{2truemm}
\includegraphics[width=0.135\textwidth]{figures/logo_Caltech}\vspace*{2truemm}
\includegraphics[width=0.135\textwidth]{figures/logo_Harvard}\vspace*{2truemm}
\includegraphics[width=0.135\textwidth]{figures/logo_IPGP}\vspace*{2truemm}
\includegraphics[width=0.112\textwidth]{figures/logo_TOTAL}\vspace*{2truemm}
\includegraphics[width=0.112\textwidth]{figures/logo_Univ_Toulouse}
\par\end{centering}
\end{figure}

>>>>

\author{$\copyright$ Princeton University (USA), CNRS and University of Marseille (France),\\
and ETH Z\"urich (Switzerland)\\
Version 2.1}

@@

\noindent \begin{centering}
\includegraphics[width=0.15\textwidth]{figures/logo_NVIDIA}\vspace*{2truemm}
\includegraphics[width=0.125\textwidth]{figures/logo_IUF}\vspace*{2truemm}
\includegraphics[width=0.135\textwidth]{figures/logo_Caltech}\vspace*{2truemm}
\includegraphics[width=0.135\textwidth]{figures/logo_Harvard}\vspace*{2truemm}
\includegraphics[width=0.135\textwidth]{figures/logo_IPGP}\vspace*{2truemm}
\par\end{centering}

\noindent \begin{centering}
\includegraphics[width=0.119\textwidth]{figures/logo_INGV}\vspace*{2truemm}
\includegraphics[width=0.119\textwidth]{figures/logo_University_of_Toronto}\vspace*{2truemm}
\includegraphics[width=0.112\textwidth]{figures/logo_Univ_Toulouse}\vspace*{2truemm}
\includegraphics[width=0.112\textwidth]{figures/logo_TOTAL}\vspace*{2truemm}
\includegraphics[width=0.130\textwidth]{figures/logo_Fairbanks}
\par\end{centering}
\end{figure}
